---
title: "Justice Hub - Summer of Data"
output: 
  html_document:
    df_print: default
    number_sections: no
    self_contained: no
    toc: no
    toc_float:
      collapsed: no
---

<br /> Last updated: `r format(Sys.time(), '%d %B, %Y')`

```{r chunk-options, include=FALSE}
# Options for building this document
knitr::opts_chunk$set(
  fig.height=5, 
  fig.width=10, 
  fig.align='center',
  echo=FALSE,
  message=FALSE,
  warning=FALSE
)
```

```{r declare-libraries}
source("libraries.R")
source("utils.R")
```


## Court Details

Court - **High Court of Madhya Pradesh**

Total Judges - 18

Accountability Partners - 

1. Sneha Rath - [Link](https://docs.google.com/spreadsheets/d/1g6zdfGi_Yo68NNRlUZO4rBfSImC8oORFuZHHq9uTeEY/edit?usp=drivesdk)
2. Biswajeet Mishra - [Link](https://docs.google.com/spreadsheets/d/1XpiynXx_RxRUz5x00qjYE603rM-vGnwk3Gw4NAJUTXM/edit?usp=drivesdk)

--- 

## Results

```{r read-judges-matrix}
judges_matrix <- readr::read_csv("../data/student_files/judges_matrix.csv")
```
```{r data-long-to-wide}
judges_matrix_wide <- judges_matrix %>% pivot_wider(names_from = var_title, values_from = var_flag)
judges_matrix_wide$judge_name <- str_to_title(judges_matrix_wide$judge_name)
```

```{r table-to-display}
var_cols <- unique(judges_matrix$var_title)
judges_matrix_wide_t <-
  judges_matrix_wide %>% select(!judge_id) %>% gt(rowname_col =  "judge_name") %>% tab_header(title = md("**Cross checking data for Judges**"), subtitle = "State: Madhya Pradesh") %>% tab_stubhead(label = "Judge Name") %>%  cols_label(Gender  =  '1',
Religion  =  '2',
Caste =  '3',
DateofBirth  =  '4',
DateofAppointment  =  '5',
DateofRetirement  =  '6',
IfDiedinOffice  =  '7',
Ifresignedfromoffice  =  '8',
IftransferredtoanyotherHighCourt  =  '9',
Dateofsuchtransfer1  =  '10',
Dateofsuchtransfer2  =  '11',
Dateofsuchtransfer3  =  '12',
IfappointedChiefJusticeinanotherHighCourt  =  '13',
IfappointedtotheSupremeCourt  =  '14',
DateofappointmenttotheSupremeCourt  =  '15',
Cadre  =  '16',
ExperienceinSubordinateJudiciary  =  '17',
LitigationExperience  =  '18',
IfaSeniorAdvocate  =  '19',
ExperienceinHighCourtAdministrativePost  =  '20',
IfservedasGovernmentCounsel  =  '21',
IfservedasAdvocateGeneral  =  '22',
IfempanelledbyPSUs  =  '23',
IfempanelledbyBanks  =  '24',
IfempanelledbyanyStatutoryBody  =  '25',
IfempanelledbyPrivateCompanies  =  '26',
ChamberDetails  =  '27',
ForeignDegreeinLaw  =  '28',
PostGraduateinanothersubject  =  '29',
PostGraduateinLaw  =  '30'
)%>% cols_width(all_of(var_cols)~px(25)) %>% tab_options(
    heading.background.color = "#F7EFB2",
    column_labels.font.size = "x-small",
    stub.font.weight = "bold",
    table.font.size = "x-small"
  ) %>% data_color(
    columns = all_of(var_cols),
    colors = scales::col_numeric(
      palette = c(colour_nomatch, colour_match , colour_NA),
      domain = c(0, 1, 2)
    )
  ) %>%   text_transform(locations = cells_body(all_of(var_cols)), fn = function(x){
    ""
  })%>% tab_style(style = list(cell_borders(
    sides = "all",
    color = "black",
    style = "dashed"
  )),
  locations = list(cells_body(columns = all_of(var_cols)))) %>% tab_style(style = list(cell_borders(
    sides = "bottom",
    color = "black",
    weight = px(3)
  )),
  locations = list(cells_column_labels(columns = gt::everything()))) %>%   tab_style(
   style = list(
      cell_fill(color = "darkblue"),
      cell_text(color = "white",align = "left")
      ),
    locations = cells_stub()
  )

judges_matrix_wide_t



```

---

### Variable List

1. Gender 
2. Religion
3. Caste 
4. Date of Birth 
5. Date of Appointment 
6. Date of Retirement 
7. If Died in Office 
8. If resigned from office 
9. If transferred to any other High Court 
10. Date of such transfer-1 
11. Date of such transfer-2 
12. Date of such transfer-3 
13. If appointed Chief Justice in another High Court 
14. If appointed to the Supreme Court 
15. Date of appointment to the Supreme Court 
16. Cadre 
17. Experience in Subordinate Judiciary 
18. Litigation Experience 
19. If a Senior Advocate 
20. Experience in High Court Administrative Post 
21. If served as Government Counsel 
22. If served as Advocate General 
23. If empanelled by PSUs 
24. If empanelled by Banks 
25. If empanelled by any StatutoryBody 
26. If empanelled by Private Companies 
27. Chamber Details 
28. Foreign Degree in Law 
29. Post Graduate in another subject 
30. Post Graduate in Law 

----







